\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry}
\geometry{margin=1in}
\title{Entropy Transfer Constraint in Cognitive Compression Systems}
\author{}
\date{}

\begin{document}
\maketitle

\section*{I. Theorem Statement}

A cognitive or computational system engaged in semantic compression will experience representational degradation or collapse if the rate of entropy intake $E_T(t)$ persistently exceeds the sum of entropy dissipation $E_D(t)$ and available internal buffering capacity $\delta(t)$, such that the cumulative overload passes a system-specific threshold $\Theta$.

\subsection*{Formal Condition}

For all time $t$:
\[
E_T(t) \leq E_D(t) + \delta(t)
\]

And if:
\[
\int_{t_0}^{t_n} (E_T(t) - E_D(t)) \, dt > \Theta \quad \Rightarrow \quad \text{System Collapse}
\]

\textbf{Where:}
\begin{itemize}
  \item $E_T(t)$: Entropy Intake — rate of incoming data or noise
  \item $E_D(t)$: Entropy Dissipation — processing, integration rate
  \item $\delta(t)$: Buffering Capacity — temporary memory or cache
  \item $\Theta$: Collapse Threshold — architecture-specific tipping point
\end{itemize}

\section*{II. Scientific Foundation}

\textbf{Thermodynamics:} Based on Landauer's Principle (minimum entropy for erasure).

\textbf{Information Theory:} Collapse occurs when entropy input exceeds dissipation capacity (Shannon entropy overload).

\textbf{Cognitive Science:} Mirrors stress-induced cognitive breakdowns.

\textbf{AI & Transformers:} Attention saturation or hallucination under overload.

\section*{III. Mechanistic Explanation}

\begin{itemize}
  \item $E_T(t)$: Entropy inflow — rate of information/data input
  \item $E_D(t)$: Internal feedback processing and entropy reduction
  \item $\delta(t)$: Finite buffering storage — decays under prolonged load
  \item $\Theta$: Collapse point — empirically observable for each architecture
\end{itemize}

\section*{IV. Testable Predictions}

\subsection*{Transformers \& LLMs}
- High-entropy input leads to semantic drift and incoherence.
- BLEU/BERT scores degrade near collapse thresholds.

\subsection*{Spiking Neural Networks}
- Overload without feedback leads to signal collapse or chaos.

\subsection*{Human Cognition}
- Working memory and feedback exhaustion causes recall failure.

\section*{V. Simulation Design Proposal}

\textbf{Model:} Transformer with entropy gating or depth controls.  
\textbf{Procedure:} Increase input entropy (shuffled syntax, noise).  
\textbf{Measures:} Track perplexity, embedding divergence, coherence.  
\textbf{Outcome:} Identify $\Theta$, observe $\delta(t)$ depletion pattern.

\section*{VI. Practical Implications}

\begin{itemize}
  \item \textbf{AI Safety:} Design feedback/regulation to prevent overload collapse.
  \item \textbf{Neuroscience:} Model stress-based failures and memory exhaustion.
  \item \textbf{Compression Theory:} Build adaptive encoders with entropy bypass.
  \item \textbf{Human Factors:} Limit cognitive load in interface and system design.
\end{itemize}

\end{document}